---
title: "testreveals"
author: qiufei
data: 2017-09-22
output:
  revealjs::revealjs_presentation:
    theme: sky
    reveal_options:
      slideNumber: true
---

## R Markdown

This is an R Markdown presentation.  For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## {data-background="01-financial-holding.jpg"}

kankan




##  {data-background=#ff0000}

Slide with R Code and Output

{data-background=#ff0000}


- Bullet 3 $$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## {data-background-iframe="https://github.com"}


## two



| we     |    |    |    |    |
|--------|----|----|----|----|
| ranhou |    |    |    |    |
|        | we | we |    | we |
|        | we | we | we |    |

## two

| Tables   |      Are      |  Cool |
|----------|:-------------:|------:|
| col 1 is |  left-aligned | $1600 |
| col 2 is |    centered   |   $12 |
| col 3 is | right-aligned |    $1 |

<div class="red2">
This text is red
</div>



